\Large Predicting how climate change will affect how and where terrestrial mammals will move in British Columbia, Canada

### 2025-04-02 writing/appendix.Rmd
changed appendix scatter plots to hex plots

```{r pred-vs-pred-hgams, fig.cap="Scatterplot of the fitted values from the HGAMs with and without including temperature for the probability of movement (\\textbf{A}) and speed when moving (\\textbf{B})."}
knitr::include_graphics('../figures/hgam-with-without-temp-prediction-agreement.png')
```

@@

```{r op, fig.cap="Relationsips between the observed and predicted values for probability of movement (\\textbf{A}) and speed given that an animal was moving (\\textbf{B}). The color in panel \\textbf{A} indicates the number of points used to calculate the estimate (on the $\\log-{2}$ scale), while the grey lines in both panels indicate perfect prediction (i.e., the 1:1 line)."}
knitr::include_graphics('../figures/p-and-speed-observed-vs-predicted.png')
```

@@

```{r pred-vs-pred-hrsfs, fig.cap="Scatterplot of the fitted values from the HRSFs with and without including temperature."}
knitr::include_graphics('../figures/hrsf-with-without-temp-prediction-agreement.png')
```

>>>>

```{r pred-vs-pred-hgams, fig.cap="Hexplot of the fitted values from the HGAMs with and without including temperature for the probability of movement (\\textbf{A}) and speed when moving (\\textbf{B})."}
knitr::include_graphics('../figures/hgam-with-without-temp-prediction-agreement.png')
```

@@

```{r op, fig.cap="Relationsips between the observed and predicted values for probability of movement (\\textbf{A}) and speed given that an animal was moving (\\textbf{B}). The color in panel \\textbf{A} indicates the number of points used to calculate the estimate (on the $\\log_{2}$ scale), while the grey lines in both panels indicate perfect prediction (i.e., the 1:1 line)."}
knitr::include_graphics('../figures/p-and-speed-observed-vs-predicted.png')
```

@@

```{r pred-vs-pred-hrsfs, fig.cap="Hexplot of the fitted values from the HRSFs with and without including temperature."}
knitr::include_graphics('../figures/hrsf-with-without-temp-prediction-agreement.png')
```
